LAGOS lake depth

### 2020-01-24 figures/01_geometry.Rmd
debugging distance outliers

dt         <- readRDS("../data/00_bathy_depth/bathy_pnts.rds")
hypso_pred <- read.csv("../data/00_hypso/hypso_predictors.csv", 
                       stringsAsFactors = FALSE) %>%
  mutate(lagoslakeid = as.character(lagoslakeid))
dt <- left_join(dt, dplyr::select(hypso_pred, lagoslakeid, reservoir_class, 
                                  buffer100m_slope_max), 
                                  by = c("llid" = "lagoslakeid"))

plot(dt$inlake_slope, dt$buffer100m_slope_max/10)

>>>>

dt         <- readRDS("../data/00_bathy_depth/bathy_pnts.rds")
hypso_pred <- read.csv("../data/00_hypso/hypso_predictors.csv", 
                       stringsAsFactors = FALSE) %>%
  mutate(lagoslakeid = as.character(lagoslakeid))
dt <- left_join(dt, dplyr::select(hypso_pred, lagoslakeid, reservoir_class, 
                                  buffer100m_slope_mean), 
                                  by = c("llid" = "lagoslakeid"))

plot(dt$inlake_slope, dt$buffer100m_slope_mean/10, 
     xlim = c(0, 3), ylim = c(0, 3))
abline(0, 1)

# View(arrange(dt, buffer100m_slope_mean))
